\Ace: Growing a Statically-Typed Language Inside a Python

### 2013-11-14 ace-pldi14/ace-pldi14.tex
Makes columns in table two lines

\section{Related Work}\label{related}
\begin{figure*}
\begin{tabular}[t]{ l | l | c c c c c }
\textbf{Approach} & \textbf{Examples} & Library & {Extensible} & Extensible & Composable & Alternative \\
\hline
Active Types & Ace & x & ~ & x & x & x\\
Desugaring & SugarJ, Sugar* & ~ & x & ~ & ~ & ~\\
Rule Injection & Qi, Typed Racket/Clojure, A? & 1+2 & ~ & x & ~ & ~\\
Static metaprogramming & Scala macros, OJ, OC++ & ~ & ~ & ~ & x & ~\\
Cross-compilation & Delite & x & ~ & ~ & ~ & x\\
EDSL frameworks & ? & x & x & x & ~ & ~\\
Type-specific literals & Wyvern & ~ & x & ~ & x & ~\\
\end{tabular}
\caption{Comparison to related approaches}
\end{figure*}
\subsection{Active Libraries}
Libraries that contain compile-time logic have been called {\it active libraries} in prior proposals \cite{activelibraries}. A number of  projects, such as Blitz++, have taken advantage of the C++ preprocessor and template-based metaprogramming system to implement domain-specific optimizations \cite{veldhuizen2000blitz++}. In Ace, we replace these brittle mini-languages with a general-purpose language and significantly expand the notion of active libraries by consideration of types as objects in the metalanguage. We thus call these types \emph{active types}.

>>>>

\section{Related Work}\label{related}
\begin{figure*}
\begin{tabular}[t]{ l | l | c c c c c }
\textbf{Approach} & \textbf{Examples} & Library & {Extensible} & Extensible & Composable & Alternative \\
\hline
Active Types & Ace & x & ~ & x & x & x\\
Desugaring & SugarJ \cite{erdweg2011sugarj}, Sugar* & ~ & x & ~ & ~ & ~\\
Rule Injection & Qi, Typed Racket \cite{TypedScheme2008}/Clojure, A? & 1+2 & ~ & x & ~ & ~\\
Static metaprogramming & Scala macros \cite{ScalaMacros2013}, OJ \cite{OpenJava2000}, OC++ \cite{OpenCpp1995}, MorphJ \cite{MorphJ2011} & ~ & ~ & ~ & x & ~\\
Cross-compilation & Delite \cite{Delite2011} & x & ~ & ~ & ~ & x\\
EDSL frameworks & ? & x & x & x & ~ & ~\\
Type-specific literals & Wyvern & ~ & x & ~ & x & ~\\
\end{tabular}
\caption{Comparison to related approaches}
\end{figure*}
\subsection{Active Libraries}
Libraries that contain compile-time logic have been called {\it active libraries} in prior proposals \cite{activelibraries}. A number of  projects, such as Blitz++, have taken advantage of the C++ preprocessor and template-based metaprogramming system to implement domain-specific optimizations \cite{veldhuizen2000blitz++}. In Ace, we replace these brittle mini-languages with a general-purpose language and significantly expand the notion of active libraries by consideration of types as objects in the metalanguage. We thus call these types \emph{active types}.
